BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-18 tex/3-algorithms.tex
Add algo1.

% Per blog procedure, inputs/output
The algorithm we are going to present in this section as for function to build an extraction rule for a relevant data of blog posts. It takes an input a set of pairs of HTML pages and target contents, and returns a extraction rule. The extraction rule should be such that when applied to one of the page, it will return data close to the target content of the corresponding page.

input : A set $pageZipTarget$ of Html page and Text target pairs
output: Best extraction rule
Q <- empty list
foreach (page, target) \in pageZipTarget do
  Q <- Q + BestExtractionRule(page, target)
return the extraction rule with highest occurrence in Q

ALGO1.

@@

2

>>>>

% Per blog procedure, inputs/output
Algorithm \ref{extraction} we are going to present in this section as for function to build an extraction rule for a relevant data of blog posts. It takes an input a set of pairs of HTML pages and target contents, and returns a extraction rule. The returned extraction rule should be such that when applied to one of the input page, the extracted text is close to the target content of the corresponding page.

\begin{algorithm}
  \caption{Best Extraction Rule}\label{extraction}
  \setstretch{1.1}
  \thinspace
  \SetKw{Of}{of}
  \SetKw{In}{in}
  \SetKwFunction{Pair}{}
  \SetKwFunction{Apply}{Apply}
  \SetKwFunction{AllRules}{AllRules}
  \SetKwFunction{Similarity}{Similarity}
  \SetKwInOut{Input}{input}
  \SetKwInOut{Output}{output}
  \DontPrintSemicolon

  \Input{Set $pageZipTarget$ of Html and Text pairs}
  \Output{Best extraction rule}
  \BlankLine
  $topRules \longleftarrow new~list$\;
  \ForEach{\Pair{page, target} \In $pageZipTarget$}{
    $score \longleftarrow new~map$\;
    \ForEach{$rule$ \In \AllRules{page}}{
      $extracted \longleftarrow$ \Apply{rule, page}\;
      $score$ \Of $rule \longleftarrow$ \Similarity{extracted, target}\;
    }
    $topRules \longleftarrow topRules$ + rule with highest $score$\;
  }
  \Return{\emph{rule with highest occurrence in} $topRules$}\;
\end{algorithm}

@@
